% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

% Must be the last line:
\usepackage[pdftex,colorlinks]{hyperref}

\begin{document}

%\newsectionwidth{1.5in}
%\sectionwidth=1.5in
%\resumewidth=8in

\name{Benjamin A. S. Riggs}
% \address used twice to have two lines of address
\address{3403 Nicollet Ave S. Apt 4, Minneapolis, MN 55408}
\address{riggs@umn.edu 612.205.9789}
 
\begin{resume}
 
\section{SUMMARY}
    System administrator skilled at providing and automating support for
    desktops and servers in a heterogeneous networked environment running a
    variety of major OSes seeks enriching position preferring open tools to
    maintain Linux servers and networking infrastructure. 
 
\section{COMPUTER \\ EXPERTISE}
    % \sl will be bold italic in New Century Schoolbook (or
    % any postscript font) and just slanted in
    % Computer Modern (default) font
    Hardware \& software support: \\
    \begin{itemize}
        \item Hundreds of desktops running Fedora and Scientific Linux.
        \item Dozens of desktops running Mac OS X and Windows.
        \item Dozens of servers running Fedora, CentOS and Scientific Linux.
    \end{itemize}
    Streamlined OS deployment, configuration and patching by migrating to
    \href{http://cobbler.github.com/}{Cobbler}, a Linux installation and
    update server: \\
    \begin{itemize}
        \item Replaced cgi-based kickstart generation with Cobbler's built-in
        tools.
        \item Replaced tar-ball distribution of system files with
        Cobbler's built-in lightweight configuration management engine.
        \item Automated software and OS updates by leveraging Cobbler's
        built-in repository management.
        \item Improved Cobbler with multiple patches for new features and
        bug-fixes.
    \end{itemize}
    Reduced hardware needs and improved reliability by implementing
    Virtual Machine hosting using KVM hypervisors managed by libvirt: \\
    \begin{itemize}
        \item Experienced with both CLI and GUI tools provided by libvirt.
        \item Migrated existing hosts to VMs.
        \item Migrated live hosts between hypervisors.
        \item Created new VMs and managed existing VMs.
    \end{itemize}
    Improved monitoring, notification and reporting services: \\
    \begin{itemize}
        \item Migrated from Nagios to Zenoss.
        \item Greatly improved monitoring and reporting coverage via
        migration.
        \item Increased granularity of automatic notifications.
        \item Tuned notification severity to be more appropriate to
        required response, eg. page and email for critical outage, email
        only for high load.
        \item Participated in on-call pager rotation.
    \end{itemize}
    Provided network management and support: \\
    \begin{itemize}
        \item Set-up and administered multiple VLANs and subnets to
        provide logical network topography as well as security.
        \item Managed both routing and non-routing firewalls on multiple
        platforms including pf, Cisco PIX, all major OSes, and various
        firmwares for consumer networking solutions.
    \end{itemize}

\section{PROFESSIONAL \\ COMMUNI- \\ CATION SKILLS}

    End user interactions: \\
    \begin{itemize}
        \item Provided appropriate level of technical detail dependent
        upon user's expertise and preferences.
        \item Interacted via RT ticketing queue, phone, in-person, and
        occasional direct email.
        \item Received verbal and written praise from users for both
        responsiveness and level of support provided.
    \end{itemize}

    Documentation: \\
    \begin{itemize}
        \item Produced documentation for new processes and technologies.
        % concise, clear, explanation, not just instruction
        % for both internal and external peers
        % code
        \item Updated and greatly improved existing documentation.
    \end{itemize}

    Peer interactions: \\
    \begin{itemize}
        \item

    \end{itemize}


    

\end{resume}
\end{document}
 
\section{EXPERIENCE} {\sl Business Applications Programmer} \hfill Fall 1990 \\
                Allied-Signal Bendix Friction Materials Division, 
                Financial Planning Department, Latham, NY
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Developed four "user friendly" forecasting 
                    systems each of which produces 18 to 139 
                    individual reports. 
                \item   Developed or improved almost all IFPS 
                    programs used for financial reports. 
                \end{itemize}
 
                {\sl Research Programmer} \hfill            Summer 1990 \\
                Psychology Department, Rensselaer Polytechnic 
                Institute 
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Performed computer aided statistical analysis 
                    of data. 
                 \end{itemize} 
                {\sl Assistant Manager} \hfill        Summers 1988-89 \\
                Thunder Restaurant, Canton, CT
                  \begin{itemize}
                   \item Recognized need for, developed, and wrote 
                    employee training manual. Performed various 
                    duties including cooking, employee training, 
                    ordering, and inventory control. 
                   \end{itemize} 
 
\section{COMMUNITY \\ SERVICE}  Organized and directed the 1988 and 1989 Grand 
                 Marshall Week \newline ``Basketball Marathon.'' A 24 hour 
                charity event to benefit the Troy Boys Club. Over 
                250 people participated each year. 

\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
            Elected {\it House Manager}, Rho Phi Sorority \\
            Elected {\it Sports Chairman} \\
            Attended Krannet Leadership Conference \\
                Headed delegation to Rho Phi Congress \\
                Junior varsity basketball team \\
                Participant, seven intramural athletic teams 
 
\section{EDUCATION} {\sl Bachelor of Science,} Interdisciplinary Science \\
                Rensselaer Polytechnic Institute, Troy, NY, 
                expected December 1990 \\
                Concentration: Computer Science \\
                Minor: Management 
