% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

% Must be the last line:
\usepackage[pdftex,colorlinks]{hyperref}

\begin{document}

%\newsectionwidth{1.5in}
%\sectionwidth=1.5in
%\resumewidth=8in

\name{Benjamin A. S. Riggs}
% \address used twice to have two lines of address
\address{3301 Elliot Ave S. Apt 1, Minneapolis, MN 55407}
\address{deisum@gmail.com 612.205.9789}
 
\begin{resume}
 
\section{SUMMARY}
    Experienced systems administrator skilled at support and automation in
    a heterogeneous networked environment seeks enriching position
    preferring to use open tools while maintaining primarily Linux-based
    servers and networking infrastructure. 
 

\section{COMPUTER \\ EXPERTISE}
    % \sl will be bold italic in New Century Schoolbook (or
    % any postscript font) and just slanted in
    % Computer Modern (default) font
    Software Support:
    \vspace{1 mm}
    \begin{itemize} \itemsep -1.5pt %reduce space between items
        \item Deployed and maintained services providing authentication
        \& authorization, file storage \& backup, network connectivity \&
        security, and web presence.
        \item Reduced hardware needs by using virtual machine and cloud
        infrastructure.
        \item Improved efficiency and consistency of software installation
        and administration by leveraging modern deployment and
        configuration management tools.
        \item Contributed patches for features and bug-fixes to upstream
        repositories.
        \item Managed and improved monitoring, notification, and reporting
        services.
        \item Administered servers and desktops with varying Linux
        distributions.
        \item Configured and maintained laptops and desktops
        running Windows and OS X.
    \end{itemize}
    \vspace{-3 mm}

    Network Management:
    \vspace{1 mm}
    \begin{itemize} \itemsep -1.5pt %reduce space between items
        \item Managed VLANs and subnets to improve network topology and
        security.
        \item Implemented and maintained border and host firewalls using
        both specialized and commodity hardware and software.
    \end{itemize}
    \vspace{-3 mm}

    Hardware Support:
    \vspace{1 mm}
    \begin{itemize} \itemsep -1.5pt %reduce space between items
        \item Determined requirements and specifications for hardware purchases.
        \item Built and repaired hardware using commodity components.
    \end{itemize}


\section{COMMUNI- \\ CATION SKILLS}

    Peer Communications:
    \vspace{1 mm}
    \begin{itemize} \itemsep -1.5pt %reduce space between items
        \item Collaborated with peers in local groups, mailing lists and
        IRC channels.
        \item Updated and created documentation focusing on concise
        explanation for configuration decisions as well as step-by-step
        instructions for set-up.
        \item Ensured documentation had appropriate level of detail for
        various audiences.
    \end{itemize}
    \vspace{-3 mm}

    End User Support:
    \vspace{1 mm}
    \begin{itemize} \itemsep -1.5pt %reduce space between items
        \item Accommodated vastly differing personalities, technical
        proficiencies, and communication styles while maintaining
        professionalism and courtesy.
        \item Received verbal and written praise from users for both
        responsiveness and level of support provided.
    \end{itemize}


\section{WORK HISTORY}
    Information Technology Professional at University of Minnesota School
    of Mathematics, Minneapolis, July 2008 to present.
    \vspace{1 mm} \\
    IT student worker at U of M School of Math, Minneapolis, January 2007
    to July 2008
    \vspace{1 mm} \\
    Bicycle Mechanic at Calhoun Cycle, Minneapolis, June 2005 to January
    2007.

\section{EDUCATION}
    University of Minnesota, courses heavily focused on physics \& math: 2006-2010.
    \vspace{1 mm} \\
    Post Secondary Enrollment Option (PSEO), University of Minnesota:
    1998-2000.
    \vspace{1 mm} \\
    University of Minnesota Talented Youth Math Program
    (\href{http://mathcep.umn.edu/umtymp/}{UMTYMP}):
    1995-2000.

\section{OTHER SKILLS \\ \& INTERESTS}
    Commuter cycling enthusiast, advocate for safe and accessible
    transportation.
    \vspace{1 mm} \\
    Extensive background in mathematics, engineering and problem-solving,
    both recreationally and formally.
    \vspace{1 mm} \\
    Python language aficionado, participant in local user group
    \href{http://www.python.mn/}{PyMNtos}. 
    \vspace{1 mm} \\
    Participant in community outreach and support activities.

\end{resume}
\end{document}
