% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

% Must be the last line:
\usepackage[pdftex,colorlinks]{hyperref}

\begin{document}

%\newsectionwidth{1.5in}
%\sectionwidth=1.5in
%\resumewidth=8in

\name{Benjamin A. S. Riggs}
% \address used twice to have two lines of address
\address{3301 Elliot Ave S. Apt 1, Minneapolis, MN 55407}
\address{deisum@gmail.com 612.205.9789}
 
\begin{resume}
 
\section{SUMMARY}
    Experienced systems administrator skilled at providing support and
    automation for desktops and servers in a heterogeneous networked
    environment seeks enriching position preferring open tools to maintain
    Linux-based servers and networking infrastructure. 
 
\section{COMPUTER \\ EXPERTISE}
    % \sl will be bold italic in New Century Schoolbook (or
    % any postscript font) and just slanted in
    % Computer Modern (default) font
    Software Services:
    \vspace{2 mm}
    \begin{itemize} \itemsep -1pt %reduce space between items
        \item Deployed and administered services providing authentication
        \& authorization, file storage \& backup, secure printing, network
        connectivity \& security, and personal \& departmental web presence.
%        \item Deployed and administered services including LDAP, kerberos,
%        NFS, samba, CUPS, rsnapshot, and apache, both from scratch and as
%        upgrades to existing services.
        \item Reduced hardware needs and replaced legacy hardware with
        virtual machines hosted by KVM hypervisors and managed by RedHat's
        libvert tool suite.
        \item Replaced legacy patch-work OS \& software installations with
        modern Linux deployment \& package management software,
        \href{http://cobbler.github.com/}{Cobbler}.
        \item Contributed to Cobbler with multiple patches for new
        features and bug-fixes.
        \item Built software packages for wide-scale deployment using RPM
        toolchain.
        \item Improved monitoring, notification, and reporting services by
        migrating from Nagios to Zenoss.
        \item Wrote and maintained administrative scripts primarily using
        Python, including migrating scripts from Perl and Bash.
    \end{itemize}

    Network Management:
    \vspace{2 mm}
    \begin{itemize} \itemsep -1pt %reduce space between items
        \item Modified multiple VLAN and subnet configuration to provide
        improved logical network topology and security on hardware from
        HP and Cisco.
        \item Implemented and managed network border firewalls with
        OpenBSD's pf and Cisco PIX.
        \item Administered host-specific firewalls with iptables and Group
        Policy.
    \end{itemize}

    Operating System Support:
    \vspace{2 mm}
    \begin{itemize} \itemsep -1pt %reduce space between items
        \item Configured and maintained dozens of servers and hundreds of
        desktops running Fedora, CentOS, and Scientific Linux.
        \item Configured and maintained dozens of laptops and desktops
        running Windows and Mac OS X.
        \item Leveraged tools to automate installation and update of
        operating systems and software packages.
    \end{itemize}

    Hardware Support:
    \vspace{2 mm}
    \begin{itemize} \itemsep -1pt %reduce space between items
        \item Determined requirements and specifications for hardware purchases.
        \item Built and repaired hardware using commodity components.
    \end{itemize}


\section{COMMUNI- \\ CATION SKILLS}

    Documentation:
    \vspace{2 mm}
    \begin{itemize} \itemsep -1pt %reduce space between items
        \item Ensured new documentation for processes and technologies
        focused on concise explanation of configuration decisions as well
        as set-by-step set-up instructions.
%        \item Created documentation for new processes and technologies
%        focusing on concise explanations for configuration decisions as
%        well as step-by-step instructions.
        \item Solicited feedback from peer-review by someone unfamiliar
        with the process or technology, and provided feedback as such.
        \item Modified documentation as appropriate for audiences of end
        users, internal customers, and peers.
%        \item Created documentation for use by end users, internal
%        customers, and peers.
        \item Updated, improved, and created documentation in code of
        administrative scripts.
    \end{itemize}

    Peer Collaboration:
    \vspace{2 mm}
    \begin{itemize} \itemsep -1pt %reduce space between items
        \item Improved understanding and familiarity of work topics and
        provided expertise by attending local peer groups as well as
        regional and national conferences.
        \item Sought assistance with my own and provided answers to
        others' challenges by leveraging mailing lists and IRC channels.
        \item Lead and participated in group discussions and
        problem-solving sessions with coworkers and peers.
        \item Participant in local Python user group,
        \href{http://www.python.mn/}{PyMNtos}. 
    \end{itemize}

    End User Support:
    \vspace{2 mm}
    \begin{itemize} \itemsep -1pt %reduce space between items
        \item Adjusted level of technical detail provided to users based
        on stated preferences and technical expertise.
        \item Supported users with technical skill levels ranging from
        complete novice to domain expert.
        \item Accommodated vastly differing personalities and communication
        styles while maintaining professionalism and courtesy.
        \item Interacted via RT ticketing system, phone, in-person, direct
        email, and instant-message.
        \item Received verbal and written praise from users for both
        responsiveness and level of support provided.
    \end{itemize}


\section{RELATED WORK HISTORY}
    Information Technology Professional at University of Minnesota School
    of Mathematics, Minneapolis, July 2008 to present.
    \vspace{1.5 mm} \\
    IT student worker at U of M School of Math, Minneapolis, January 2007
    to July 2008
    \vspace{1.5 mm} \\
    Bicycle Mechanic at Calhoun Cycle, Minneapolis, June 2005 to January
    2007.

\section{EDUCATION}
    Various classes at University of Minnesota, including graduate level
    courses in physics \& math, January 2006 to May 2010.
    \vspace{1.5 mm} \\
    Iowa State University, 2000 to 2001.
    \vspace{1.5 mm} \\
    Post Secondary Enrolment Option (PSEO): University of Minnesota,
    1998-2000.
    \vspace{1.5 mm} \\
    University of Minnesota Talented Youth Math Program (UMTYMP):
    1995-2000.
    \vspace{1.5 mm} \\
    Eden Prairie High School, Class of 2000.

\section{OTHER SKILLS \\ \& INTERESTS}
    Transportation cycling enthusiast and year-round cyclist, despite
    challenges imposed by widely varying weather conditions throughout the
    year, particularly winter.
    \vspace{1.5 mm} \\
    Extensive problem solving experience from life-long aptitude in
    mathematics; numerous mathematics, physics and engineering courses;
    years of bicycle maintenance and repair; and growing up playing with
    LEGOs, BRIO trains, puzzles, and other toys.
    \vspace{1.5 mm} \\
    Avid interest, thorough understanding, and recreational use of Python
    programming language.
    \vspace{1.5 mm} \\
    Actively participated in community-building activities such as Habitat
    for Humanity, Appalachian Service Project, and Make a Difference Day,
    as well as local bicycling-community events and advocacy.

\end{resume}
\end{document}
