% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

% Must be the last line:
\usepackage[pdftex,colorlinks]{hyperref}

\begin{document}

%\newsectionwidth{1.5in}
%\sectionwidth=1.5in
%\resumewidth=8in

\name{Benjamin A. S. Riggs}
% \address used twice to have two lines of address
\address{3301 Elliot Ave S. Apt 1, Minneapolis, MN 55407}
\address{deisum@gmail.com 612.205.9789}
 
\begin{resume}
 
\section{SUMMARY}
    Experienced and self-motivated systems administrator and technology
    enthusiast skilled at maintaining a variety of hardware and software
    systems seeks enriching position supporting a variety of technologies
    in a dynamic and engaging environment.

\section{COMPUTER \\ EXPERTISE}
    % \sl will be bold italic in New Century Schoolbook (or
    % any postscript font) and just slanted in
    % Computer Modern (default) font

    Hardware Support:
    \vspace{2 mm}
    \begin{itemize} \itemsep -1pt %reduce space between items
        \item Determined requirements and specifications for hardware purchases.
        \item Built and repaired computer hardware using commodity components.
        \item Configured and maintained a variety of peripheral devices
        using both vendor-supplied and custom tool-chains.
        \item Analyzed malfunctioning systems to determine source of
        failure and repaired or replaced components as necessary.
    \end{itemize}

    Software Services:
    \vspace{2 mm}
    \begin{itemize} \itemsep -1pt %reduce space between items
        \item Deployed and administered services providing authentication
        \& authorization, file storage \& backup, secure printing, network
        connectivity \& security, and personal \& departmental web presence.
        \item Reduced hardware needs and replaced legacy hardware with
        virtual machines.
        \item Replaced legacy, custom software tools with supported,
        modern solutions.
        \item Built software packages for wide-scale deployment and ease
        of administration.
        \item Wrote and maintained administrative scripts using a variety
        of programming languages.
    \end{itemize}

    Network Management:
    \vspace{2 mm}
    \begin{itemize} \itemsep -1pt %reduce space between items
        \item Setup and maintained wireless and wired networks with a
        variety of topologies tailored to suit requirements.
        \item Maintained network security and segregation with hardware
        and software firewalls.
        \item Protected individual computers with OS-provided client
        firewalls.
    \end{itemize}

    Operating System Support:
    \vspace{2 mm}
    \begin{itemize} \itemsep -1pt %reduce space between items
        \item Configured and maintained dozens of servers and hundreds of
        desktops running several flavors of Linux.
        \item Configured and maintained dozens of laptops and desktops
        running Windows and Mac OS X.
        \item Leveraged tools to automate installation and update of
        operating systems and software packages.
    \end{itemize}


\section{COMMUNI- \\ CATION SKILLS}

    End User Support:
    \vspace{2 mm}
    \begin{itemize} \itemsep -1pt %reduce space between items
        \item Adjusted level of technical detail provided to users based
        on stated preferences and technical expertise.
        \item Supported users with technical skill levels ranging from
        complete novice to domain expert.
        \item Accommodated vastly differing personalities and communication
        styles while maintaining professionalism and courtesy.
        \item Interacted via RT ticketing system, phone, in-person, direct
        email, and instant-message.
        \item Received verbal and written praise from users for both
        responsiveness and level of support provided.
    \end{itemize}

    Documentation:
    \vspace{2 mm}
    \begin{itemize} \itemsep -1pt %reduce space between items
        \item Ensured new documentation for processes and technologies
        focused on concise explanation of configuration decisions as well
        as set-by-step instructions.
        \item Solicited feedback from peer-review by someone unfamiliar
        with the process or technology, and provided feedback as such.
        \item Modified documentation as appropriate for audiences of end
        users, internal customers, and peers.
        \item Updated, improved, and created documentation in code of
        administrative scripts.
    \end{itemize}

    Peer Collaboration:
    \vspace{2 mm}
    \begin{itemize} \itemsep -1pt %reduce space between items
        \item Improved understanding and familiarity of work topics and
        provided expertise by attending local peer groups as well as
        regional and national conferences.
        \item Sought assistance with my own and provided answers to
        others' challenges by leveraging mailing lists and IRC channels.
        \item Lead and participated in group discussions and
        problem-solving sessions with coworkers and peers.
        \item Participant in local Python user group,
        \href{http://www.python.mn/}{PyMNtos}. 
    \end{itemize}


\section{RELATED WORK HISTORY}
    Information Technology Professional at University of Minnesota School
    of Mathematics, Minneapolis, July 2008 to present.
    \vspace{1.5 mm} \\
    IT student worker at U of M School of Math, Minneapolis, January 2007
    to July 2008
    \vspace{1.5 mm} \\
    Bicycle Mechanic at Calhoun Cycle, Minneapolis, June 2005 to January
    2007.

\section{EDUCATION}
    Various classes at University of Minnesota, including graduate level
    courses in physics \& mathematics, January 2006 to May 2010.
    \vspace{1.5 mm} \\
    CompTIA A+ certification, 2005
    \vspace{1.5 mm} \\
    Iowa State University, 2000 to 2001.
    \vspace{1.5 mm} \\
    Post Secondary Enrolment Option (PSEO): University of Minnesota,
    1998-2000.
    \vspace{1.5 mm} \\
    University of Minnesota Talented Youth Math Program (UMTYMP):
    1995-2000.
    \vspace{1.5 mm} \\
    Eden Prairie High School, Class of 2000.

\section{OTHER SKILLS \\ \& INTERESTS}
    Transportation cycling enthusiast and year-round cyclist, despite
    challenges imposed by widely varying weather conditions throughout the
    year, particularly winter.
    \vspace{1.5 mm} \\
    Extensive problem solving experience from life-long aptitude in
    mathematics; numerous mathematics, physics and electrical engineering
    courses; years of bicycle maintenance and repair; and as a child
    playing with LEGO, wooden trains, puzzles, and similar toys.
    \vspace{1.5 mm} \\
    Avid interest, thorough understanding, and recreational use of Python
    programming language.
    \vspace{1.5 mm} \\
    Actively participated in community-building activities such as Habitat
    for Humanity, Appalachian Service Project, and Make a Difference Day,
    as well as local bicycling-community events and advocacy.

\end{resume}
\end{document}
