% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

% Must be the last line:
\usepackage[pdftex,colorlinks]{hyperref}

\begin{document}

%\newsectionwidth{1.5in}
%\sectionwidth=1.5in
%\resumewidth=8in

\name{Benjamin A. S. Riggs}
% \address used twice to have two lines of address
\address{1406 Spruce Pl. Apt 5, Minneapolis, MN 55403}
\address{deisum@gmail.com 612.205.9789}
 
\begin{resume}
 
\section{SUMMARY}
    Experienced systems administrator and engineer adept at design,
    automation and support of heterogeneous environments seeks dynamic
    position, preferring the use of open tools, to leverage primarily
    Linux-based infrastructure. 
 

\section{COMPUTER \\ EXPERTISE}
    % \sl will be bold italic in New Century Schoolbook (or
    % any postscript font) and just slanted in
    % Computer Modern (default) font
    Software:
    \vspace{1 mm}
    \begin{itemize} \itemsep -1.5pt %reduce space between items
        \item Designed, deployed and maintained services providing
        authentication \& authorization, data storage, secure
        connectivity, and web presence.
        \item Managed virtual machine and cloud infrastructure to mitigate
        hardware needs.
        \item Improved efficiency and consistency of software installation
        and administration by leveraging modern deployment and
        configuration management tools.
        \item Contributed patches for features and bug-fixes to upstream
        repositories.
        \item Designed, managed and improved monitoring and notification
        services.
        \item Deployed and administered servers, desktops, and laptops
        running various flavors of Linux, Windows, and OS X.
    \end{itemize}
    \vspace{-3 mm}

    Networking:
    \vspace{1 mm}
    \begin{itemize} \itemsep -1.5pt %reduce space between items
        \item Managed physical and logical networks to improve topology
        and security.
        \item Implemented and maintained border and host firewalls using
        both specialized and commodity hardware and software.
    \end{itemize}
    \vspace{-3 mm}

    Hardware:
    \vspace{1 mm}
    \begin{itemize} \itemsep -1.5pt %reduce space between items
        \item Determined requirements and specifications for hardware purchases.
        \item Built and repaired hardware using commodity components.
    \end{itemize}


\section{COMMUNI- \\ CATION SKILLS}

    Peer Communications:
    \vspace{1 mm}
    \begin{itemize} \itemsep -1.5pt %reduce space between items
        \item Collaborated with peers in local groups, mailing lists and
        IRC channels.
        \item Updated and created documentation focusing on concise
        explanation for configuration decisions as well as step-by-step
        instructions for set-up.
        \item Ensured documentation had appropriate level of detail for
        various audiences.
    \end{itemize}
    \vspace{-3 mm}

    End User Support:
    \vspace{1 mm}
    \begin{itemize} \itemsep -1.5pt %reduce space between items
        \item Accommodated vastly differing personalities, technical
        proficiencies, and communication styles while maintaining
        professionalism and courtesy.
        \item Received verbal and written praise from users for both
        responsiveness and level of support provided.
    \end{itemize}


\section{WORK HISTORY}
    Solutions Architect \& Engineer for Synaptic Design, April 2014 to present.
    \vspace{1 mm} \\
    Systems Administrator at University of Minnesota School of
    Mathematics, as Student Worker January 2007 to July 2008, IT Professional
    through May 2014.
%    \vspace{1 mm} \\
%    IT student worker at U of M School of Math, Minneapolis, January 2007
%    to July 2008
    \vspace{1 mm} \\
    Bicycle Mechanic and Sales at Calhoun Cycle, Minneapolis, June 2005 to
    January 2007.

\section{EDUCATION}
    University of Minnesota, courses heavily focused on physics \& math: 2006-2010.
    \vspace{1 mm} \\
    Post Secondary Enrollment Option (PSEO), University of Minnesota:
    1998-2000.
    \vspace{1 mm} \\
    University of Minnesota Talented Youth Math Program
    (\href{http://mathcep.umn.edu/umtymp/}{UMTYMP}):
    1995-2000.

\section{OTHER SKILLS \\ \& INTERESTS}
    Commuter cyclist and enthusiast, advocate for safe and accessible
    transportation.
    \vspace{1 mm} \\
    Extensive background in mathematics, engineering and problem-solving,
    both recreationally and formally.
    \vspace{1 mm} \\
    Python language aficionado, participant in local user group
    \href{http://www.python.mn/}{PyMNtos}. 
    \vspace{1 mm} \\
    Participant in community outreach and support activities.

\end{resume}
\end{document}
