% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\usepackage[pdftex,colorlinks]{hyperref}

\begin{document}

\signature{Benjamin Riggs}                 % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter} %{Ms. Terri Roberts \\
%Senior Staff Recruiter \\
%XYZ Corporation \\
%Rt. 56 \\
%Anytown, New Jersey 05867}


\begin{flushleft}
{\large\bf Benjamin A. S. Riggs}
\end{flushleft}
\vskip 2pt
\nointerlineskip	% hrules only listen to \hoffset, so I have this code	  
\moveleft\hoffset\vbox{\hrule width\textwidth} 
\nointerlineskip
\vskip 2pt
%\medskip\hrule height 1pt
\leavevmode\hbox to \textwidth
  {\hfill\vbox{\hbox{1406 Spruce Pl. Apt 5, Minneapolis, MN 55403}
       \hbox{deisum@gmail.com 612.205.9789}
      }%
  }\par
\vfill % forces letterhead to top of page

\noindent As a skilled systems administrator with experience leveraging
and managing a variety of virtualization platforms, I believe I would be
particularly well-suited for the position of Cloud Reliability Engineer.

\noindent My passion for solving problems (and puzzles: some friends and I
bested the \href{http://riddle-room.com/about/}{Riddle Room} in record
time) motivates me to discover and solve the root cause of a problem, not
just find a work-around. Additionally, I am skilled at creating
connections between disparate systems, enabling them share infrastructure
or data, which is key to improving automation and deployment tools. I'm
excited by the prospect of working on challenging and diverse problem sets
to improve upon existing solutions or find new ones.

\noindent Over the past 9 months I've had the wonderful fortune of working with a
small group of friends to develop some incredibly awesome projects.
Unfortunately, due to a lack of projected growth (and what I consider poor
business decisions by the owners), the company doesn't have enough work to
keep me suitably employed, which is why I'm seeking other employment.
Creative problem solving is at the core of the work I have been doing, a
talent developed through a life-long love of seeking new challenges and
how they engage my mind, and a skill I'm excited to bring to new
endeavors.

\noindent For additional information about my skills and experience, please refer to
my r\'{e}sum\'{e}. Thank you for your consideration.
 
\closing{Sincerely,} 
 
%\encl{}  				% Enclosures

\vfill      % matches \vfill above to ~center text in page

\pagenumbering{gobble}  % Remove page numbers (and reset to 1)

\end{letter}
 

\end{document}






