% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

% Must be the last line:
\usepackage[pdftex,colorlinks]{hyperref}

\begin{document}

%\newsectionwidth{1.5in}
%\sectionwidth=1.5in
%\resumewidth=8in

\input{header}
 
\begin{resume}
 
\section{SUMMARY}
    % I want to solve interesting, complex problems, mostly with software.
    Software Engineer with a background of systems integration and
    administration in heterogeneous environments seeks opportunity to
    further develop architectural skills while leveraging existing
    knowledge and abilities to provide dynamic solutions to a diverse
    range of challenges.


%    % Python specific
%    Knowledgeable Python engineer with background in integration and
%    administration of hardware and software systems in heterogeneous
%    environments seeks opportunity to further develop software architecture
%    and engineering ability while leveraging extensive language knowledge
%    and adept problem-solving skills.


\section{TECHNICAL \\ EXPERTISE}
    % \sl will be bold italic in New Century Schoolbook (or
    % any postscript font) and just slanted in
    % Computer Modern (default) font

    Software Engineering:
    \vspace{1 mm}
    \begin{itemize}
        %\itemsep -1.5pt % Reduce space between items
        \item Designed and deployed APIs used in production services,
            including local libraries as well as RESTful remote access.
        \item Created integrated database architecture and interfaces for
            relational and key-value databases.
        \item Leveraged existing APIs, both local \& remote, to create
            interoperability and data passage between disparate systems,
            both vendor supplied and open-source.
        \item Applied focus on usability as well as functionality to
            designs of User Interfaces, including GUIs, CLIs, APIs, and
            hardware interactions.
        \item Evaluated available frameworks and existing software
            solutions relevant to the problem domain to select and
            implement the best approach in balancing project requirements
            and accessible resources.
        \item Ensured source code security and enabled developer
            collaboration by using Version Control Systems, distributed
            and not.
        \item Contributed feedback and patches for features and bug-fixes
            to upstream open-source repositories.
        \item Maintained high levels of code reuse and readability by
            leveraging design patterns and strategies to help ensure
            proper separation of concerns and modularity.
        \item Advanced knowledge and experience with Python, intermediate
            to novice skill with bash, JavaScript, C, .NET, PHP, PowerShell,
            Java.
    \end{itemize}

    Systems Integration and Administration:
    \vspace{1 mm}
    \begin{itemize}
        \item Designed, deployed, and maintained services providing
            user authentication \& authorization, file storage \& backup,
            network connectivity \& security, and web presence.
        \item Configured system interoperability to provide access to user
            data between disparate operating systems.
        \item Managed virtual machine and cloud infrastructure to mitigate
            hardware needs using a variety of commercial providers as well
            as internal services.
        \item Integrated custom hardware and software with commercial
            solutions to create new functionality and novel application.
        \item Improved efficiency and consistency of software installation
            and administration by leveraging modern deployment and
            configuration management tools.
        \item Designed, managed and improved monitoring and notification
            services by moving to a modern software solution and creating
            custom plugins.
        \item Managed physical and logical networks to improve topology
            and security.
        \item Implemented and maintained border and host firewalls using
            both specialized and commodity hardware and software.
        \item Procured, repaired, managed, and deployed server and
            consumer hardware.
    \end{itemize}

\section{COMMUNI- \\ CATION SKILLS}

    Peer Communications:
    \vspace{1 mm}
    \begin{itemize}
        %\itemsep -1.5pt %reduce space between items
        \item Collaborated with peers in local groups, mailing lists and
            IRC channels.
        \item Presented unique solutions to challenges for professional
            and enthusiast groups.
        \item Exhibited interactive systems consisting of integrated custom
            \& commercial hardware \& software and facilitated public use
            of the system.
        \item Updated and created documentation focusing on concise
            explanation for design decisions as well as detailed usage
            instructions.
        \item Ensured documentation had appropriate level of detail for
            various audiences.
    \end{itemize}
    %\vspace{-3 mm}

    User Support:
    \vspace{1 mm}
    \begin{itemize}
        %\itemsep -1.5pt %reduce space between items
        \item Accommodated vastly differing personalities, technical
            proficiencies, and communication styles while maintaining
            professionalism and courtesy.
        \item Received verbal and written praise from users for both
            responsiveness and level of support provided.
    \end{itemize}


\input{work_history}

\input{education}

\input{other_skills}

\end{resume}
\end{document}
